Determination of Center of Rotation \\ in Computed Tomography

### 2017-07-13 seminar_cor/seminar_cor_haegele.tex
added ligature package

% my own stuff
\newcommand{\xray}{X-ray~}
\newcommand{\xrays}{X-rays~}
\usepackage{cleveref}

@@

>>>>

% my own stuff
\newcommand{\xray}{X-ray~}
\newcommand{\xrays}{X-rays~}
\usepackage{cleveref}
\usepackage{cmap}
\usepackage{csquotes}

@@

Unfortuantely, parallel beam geometry is impractical as a pencil beam \xray source (source emmiting only one ray in a specific direction) would have to be moved parallel to the detector to collect all samples for a single rotation angle, which is very time consuming.
However, parallel beam geometry occurs at synchrotron facilities \cite{something}.
